A simplified dynamic bioenergetic model for coral-algal symbiosis and coral bleaching

### 2016-10-26 JTB_ms/JTB_ms.Rmd
Fig4-7 captions

![Figure 4. Light-driven seasonal dynamics of symbiont abundance and coral growth. Light input (upper panel) was designed as a sinusoidal curve with a period of one year, with maximum and minimum values of 40 and 22 mol photons m^-2^ d^-1^, based on @Stimson:1997p3837. The dynamic behavior of symiont to host biomass ratio (middle panel) and the specific growth rate of host biomass (lower panel) show seasonal oscillations that are greater in magnitude under higher nutrients (1e-5 molN L^-1^; dashed lines) relative to lower nutrients (1e-7 molN L^-1^; solid lines), consistent with the findings of @Stimson:1997p3837. Prey density was set at 1e-5 CmolX L^-1^.](../img/Fig4.png)

@@

![Figure 5. Bleaching.](../img/Fig5.png)

@@

![Figure 6. Bleaching and interactive factors.](../img/Fig6.png)

@@

![Figure 7. Hysteresis.](../img/Fig7.png)

>>>>

![Figure 4. Light-driven seasonal dynamics of symbiont abundance and coral growth. Light input (upper panel) was designed as a sinusoidal curve with a period of one year, with maximum and minimum values of 40 and 20 mol photons m^-2^ d^-1^, based on @Stimson:1997p3837. The dynamic behavior of symiont to host biomass ratio (middle panel) and the specific growth rate of host biomass (lower panel) show seasonal oscillations that are greater in magnitude under higher nutrients (1e-6 molN L^-1^; dashed lines) relative to lower nutrients (1e-7 molN L^-1^; solid lines), consistent with the findings of @Stimson:1997p3837. Prey density was set at 1e-5 CmolX L^-1^.](../img/Fig4.png)

@@

![Figure 5. Coral bleaching as a switch from a nitrogen- to carbon-limited alternative stable state. This transition is demonstrated in response to gradually increasing external light (A), which causes an increase in production of ROS (B) that reduces the photosynthetic rate through photoinhibition (C). Decreasing photosynthesis moves the system from overall nitrogen-limitation toward carbon-limitation (D); when this threshold is crossed, the system rapidly becomes highly carbon-limited as photosynthesis becomes CO~2~-limited (E) and symbiont densities rapidly decline (F) into a bleached state. (All parameters at default values; external DIN=1e-7 molN/L, prey density=0).](../img/Fig5.png)

@@

![Figure 6. Bleaching with interactive factors. Simulations of high light stress (sinusoid with maximum=39 mol ph m^-2^ d^-1^) under default environmental conditions (solid line; DIN=1e-7 molN/L; prey=3e-6 CmolX/L), or with elevated feeding (dashed line; prey=6e-6 CmolX/L), or elevated nutrients (dotted line; DIN=1e-6 molN/L). Initial symbiont biomass was set to the steady state for each set of starting conditions, respectively. (All parameters set to default values).](../img/Fig6.png)

@@

![Figure 7. Hysteresis in coral bleaching and recovery. The symbiont:host biomass ratio is plotted as a function of light from a simulation of linearly increasing, then decreasing, external light. The direction of the trajectory is indicated with arrowheads evenly spaced with respect to time. The rate of change in light was slow (0.005 mol ph d^-1^) such that dynamics track closely to steady state values. (All parameters at default values; DIN=2e-7 molN/L; Prey=2e-6 CmolX/L).](../img/Fig7.png)
